Markowitz Portfolio Optimization with Inflation

### 2023-12-19 paper/paper.tex
[PR] Fix issues with latex and requirements, as discussed during code review
[md, latex, codeformat] Update latex to include reference to the original Markowitz work, fix formatting

This paper delves into the realm of portfolio optimisation using the renowned Markowitz framework, explicitly focusing on navigating the complexities of an inflationary environment. Rather than adhering to conventional wisdom, our methodology begins with a comprehensive analysis of various asset classes to discern their correlation with inflation. Recognising that not all assets respond uniformly to inflationary pressures, we aim to identify and select those that weather the storm and offer a shield against rising prices' corrosive effects.

@@

Building on this foundation, we apply the Markowitz portfolio optimisation model. Recognising that optimal portfolios are not one-size-fits-all, we tailor our approach to fixed-income unique characteristics of inflation-sensitive assets. Through a judicious combination of these assets, we aim to construct portfolios that maximise returns and, crucially, hedge against the eroding effects of inflation.

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=1\textwidth]{paper/figure/CPI_Returns.pdf}
    \caption{Facet Grid of each Asset Class against the CPI.}
    \label{fig:mesh6}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{paper/figure/Cointegration_Matrix.pdf}
    \caption{Cointegration Matrix.}
    \label{fig:mesh3}
\end{figure}

@@

The heart of Markowitz's theory is the "Efficient Frontier," a graphical representation showing the optimal set of portfolios providing the maximum possible expected return for a given level of risk. Portfolios that lie below the efficient frontier are sub-optimal because they do not provide enough return for the level of risk they carry.

@@

In Markowitz's framework, risk is quantified as the standard deviation of portfolio returns, a measure of variability in returns. Return is the expected return of the portfolio, a weighted sum of the expected returns of the individual assets.

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=1\textwidth]{paper/figure/PNL.pdf}
    \caption{Cumulative Returns.}
    \label{fig:mesh4}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=1\textwidth]{paper/figure/Optimal_PF.pdf}
    \caption{Optimal Portfolio with Efficient Frontier.}
    \label{fig:mesh5}
\end{figure}

@@

>>>>

This paper delves into the realm of portfolio optimisation using the renowned Markowitz framework \cite{markowitz1952}, explicitly focusing on navigating the complexities of an inflationary environment. Rather than adhering to conventional wisdom, our methodology begins with a comprehensive analysis of various asset classes to discern their correlation with inflation. Recognising that not all assets respond uniformly to inflationary pressures, we aim to identify and select those that weather the storm and offer a shield against rising prices' corrosive effects.

@@

Building on this foundation, we apply the Markowitz portfolio optimisation model \cite{markowitz1952}. Recognising that optimal portfolios are not one-size-fits-all, we tailor our approach to fixed-income unique characteristics of inflation-sensitive assets. Through a judicious combination of these assets, we aim to construct portfolios that maximise returns and, crucially, hedge against the eroding effects of inflation.

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=1\textwidth]{figure/CPI_Returns.pdf}
    \caption{Facet Grid of each Asset Class against the CPI.}
    \label{fig:mesh6}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\textwidth]{figure/Cointegration_Matrix.pdf}
    \caption{Cointegration Matrix.}
    \label{fig:mesh3}
\end{figure}

@@

The heart of Markowitz's theory \cite{markowitz1952} is the "Efficient Frontier," a graphical representation showing the optimal set of portfolios providing the maximum possible expected return for a given level of risk. Portfolios that lie below the efficient frontier are sub-optimal because they do not provide enough return for the level of risk they carry.

@@

In Markowitz's framework \cite{markowitz1952}, risk is quantified as the standard deviation of portfolio returns, a measure of variability in returns. Return is the expected return of the portfolio, a weighted sum of the expected returns of the individual assets.

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=1\textwidth]{figure/PNL.pdf}
    \caption{Cumulative Returns.}
    \label{fig:mesh4}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=1\textwidth]{figure/Optimal_PF.pdf}
    \caption{Optimal Portfolio with Efficient Frontier.}
    \label{fig:mesh5}
\end{figure}

@@

% References
\begin{thebibliography}{9}

\bibitem{markowitz1952}
Markowitz, H. (1952).
\textit{Portfolio Selection}.
The Journal of Finance, 7(1), 77-91.

\end{thebibliography}
